\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
%\usepackage{inconsolata}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[parfill]{parskip}
\usepackage[margin = 2.5cm]{geometry}

\usepackage[T1]{fontenc}


\begin{document}

\title{Assignment 2: AWS API\\ IN720 Virtualisation}
\date{}
\maketitle

\section*{Introduction}
We have discussed how the widespread use of virtualisation means that servers have become things with which we interact via an API. In this assignment you will write a program that will create, start, stop, terminate, and report the status of an EC2 instance.

AWS lets us assign \emph{tags} to instances, basically key-value text pairs. We will use a tags to identify our instances. Tag your instance with your surname.

\section{Program specifications}
Write a program that takes one command line argument and acts according to the following specifications:

\begin{description}
  \item{\texttt{start}} If an instance with your tag exists, your program shall start it.  If not, then create and run the instance. Create your instance in the \texttt{us-west-1} zone using the \texttt{ami-31490d51} image. Use a \texttt{t2.nano} insstance type.
  
  \item{\texttt{stop}} Your program shall stop the instance.
  
  \item{\texttt{status}} Your program shall report the instance's  \texttt{status} value.
  
  \item{\texttt{stop}} Your program shall stop the instance.
  
  \item{\texttt{terminate}} Your program shall terminate the instance.

\end{description}

\section{Submission and marking} 

This assignment is worth 20\% of your course mark and it is due at the beginning of class on Tuesday, 11 October. Place your program files in a GitHub repository named \texttt{in720-assignment2}. It will be marked according to the following criteria:

\begin{itemize}
  \item Functional correctness (50 marks)
  \item Code quality and origanisation (40 marks)
  \item Sensible documentation and commenting (10 marks)
  \end{itemize}
  
  Be sure that your files are pushed to your \texttt{master} branch on your GitHub repository on or before the dues date and time. 
 
\end{document}